Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-23 Draft.Rmd
ppp

```{r ExploratoryAnalysis}
set.seed(123)
# Split origin dataset into 80/20
dat_split <- initial_split(origin, prop =.8)
dat_split
# Use 80% of data for training 
train <- training(dat_split)
test <- data[dat_split==1, ]

@@

```{r}
# Create table of prediction metrics
linreg = res1 |> collect_metrics() |> as.data.frame()
linreg = cbind(linreg[,1], round(linreg[,3],2))
knn = res2 %>% collect_metrics() |> as.data.frame()
knn = cbind(knn[,1], round(knn[,3],2))
xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
xgboost = cbind(xgboost[,1], xgboost[,3])
ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
ranfor = cbind(ranfor[,1], ranfor[,3])

compare = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg,knn,xgboost,ranfor))
colnames(compare) = c('model','estimator','estimate') 
compare = as.data.frame(compare) |> pivot_wider(names_from=estimator, values_from=estimate)
tibble(compare)
```

>>>>

```{r ExploratoryAnalysis}
set.seed(123)
# Split origin dataset into 80/20
dat_split <- initial_split(origin, prop =.8)
dat_split
# Use 80% of data for training 
train <- training(dat_split)
test <- testing(dat_split)

@@

```{r}
# Create table of prediction metrics from training data
linreg1 = res1 |> collect_metrics() |> as.data.frame()
linreg1 = cbind(linreg1[,1], round(linreg1[,3],2))
knn1 = res2 %>% collect_metrics() |> as.data.frame()
knn1 = cbind(knn1[,1], round(knn1[,3],2))
xgboost1 = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
xgboost1 = cbind(xgboost1[,1], xgboost1[,3])
ranfor1 = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
ranfor1 = cbind(ranfor1[,1], ranfor1[,3])

compare1 = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg1,knn1,xgboost1,ranfor1))
colnames(compare1) = c('model','estimator','estimate') 
compare1 = as.data.frame(compare1) |> pivot_wider(names_from=estimator, values_from=estimate)
tibble(compare1)

# Get pred. metrics from models based on testing data
# LR

# KNN

# XGB

# RF

```
